%\newpage\subsection*{Design and Development of the Artefact}\label{appendix:devArt}

%\subsubsection*{Coding}
\begin{lstlisting}[language=java,label=activity_call_on_btn_press,lineskip={0pt}, caption=Activity Call on Button Press, basicstyle=\scriptsize, captionpos=b]
    btn.setOnClickListener(new View.OnClickListener() {
        @Override
        public void onClick(View view) {
            String nextStep = GetNextExperimentStepUseCase.getInstance().getNextExperimentStep();
            try {
                Class<?> c = Class.forName(nextStep);
                Intent intent = new Intent(ChooseTestSubjectActivity.this, c);

                startActivity(intent);
            } catch (ClassNotFoundException e) {
                System.out.println("Error " + e.getMessage());
            }
        }
    });
\end{lstlisting}

\subsubsection*{Use Cases}
\begin{itemize}
    \item \textbf{GetNextActivity}: (\textit{Load next experiment step}) Get the next step of the experiment from the experiment data.
    \item \textbf{GetParticipantDataUseCase}: (\textit{Load Participant Data}) Get all participants IDs or names from the participant data. 
    \item \textbf{CreateNewParticipantUseCase}: (\textit{Create New Participant}) Create a new participant ID or name in the participant data.
    \item \textbf{GetGroupAllocationPUseCase}: (\textit{Read Group Allocation Participant}) Get the manual group allocation for a specific participant from the participant data.
    \item \textbf{GetGroupAllocationEUseCase}: (\textit{Read Group Allocation Experiment}) Get the general group allocation from the experiment data.
    \item \textbf{AllocateGroupsUseCase}: (\textit{Allocate Groups}) Allocate groups automatically and save the respective group allocation for every participant ID or name in the particpant data. 
    \item \textbf{SetGroupAllocationPUseCase}: (\textit{Save group allocation}) Save the new group allocation in the participant file for the respective participant.
    \item \textbf{GetNextDataEntryUseCase}: (\textit{Load next entry of data for participant}) Get next data entry for a participant ID or name from the participant data. 
    \item \textbf{InsertDataPUseCase}: (\textit{Insert Missing Data Entry}) Save a data entry for a corresponding participant ID or name in the participant data.
    \item \textbf{LogMetaDataUseCase}: (\textit{Log meta data}) Save meta data from the current process step in the experiment data.
    \item \textbf{GetInfoScreenDataUseCase}: (\textit{Load info screen data}) Get information that should be displayed from the experiment data.  
    \item \textbf{SetCurrentParticipant}: (\textit{Set current participant}) Set the participant that currently performs the experiment.  
    \item \textbf{GetCurrentParticipant}: (\textit{Get current participant}) Get the participant that currently participates in the experiment.  
\end{itemize}